---
title: "2002-2016_table_updates"
author: "Gavin Lemley"
date: "April 5, 2019"
output: html_document
---

Load in data and libraries
```{r setup, include=FALSE}
library(tidyverse)
root.dir <- rprojroot::find_root("Chem_database_mgmt.Rproj")

simpleRIBS <- read.csv(file.path(root.dir, "data/source", "simpleRIBS.csv"), stringsAsFactors = FALSE)
# historicRIBS <- read.csv("C:/Data/RIBS/From_L_drive/RIBS.csv", stringsAsFactors = FALSE)

```

Analyze for completeness issus
```{r}

# Look at number of samples by year and parameter
simpleRIBS$SAMPLE_DATE <- as.Date(simpleRIBS$SAMPLE_DATE, "%Y-%m-%d")
simpleRIBS$year <- lubridate::year(simpleRIBS$SAMPLE_DATE)

count.yr.param <- simpleRIBS %>%
        group_by(year, Parameter) %>%
        tally()
count.yr <- simpleRIBS %>%
        group_by(year) %>%
        tally()

sites.2007 <- simpleRIBS %>% 
  filter(year == 2007)
sites.2007 <- unique(sites.2007$Station.Name)

sites.2008 <- simpleRIBS %>% 
  filter(year == 2008)
sites.2008 <- unique(sites.2008$Station)

sites.2009 <- simpleRIBS %>% 
  filter(year == 2009) 
sites.2009 <- unique(sites.2009$Station)

sites.2010 <- simpleRIBS %>% 
  filter(year == 2010) 
sites.2010 <- unique(sites.2010$Station)

sites.2011 <- simpleRIBS %>% 
  filter(year == 2011) 
sites.2011 <- unique(sites.2011$Station)

sites.2012 <- simpleRIBS %>% 
  filter(year == 2012) 
sites.2012 <- unique(sites.2012$Station)

sites.2013 <- simpleRIBS %>% 
  filter(year == 2013) 
sites.2013 <- unique(sites.2013$Station)

sites.2014 <- simpleRIBS %>% 
  filter(year == 2014) 
sites.2014 <- unique(sites.2014$Station)

sites.2015 <- simpleRIBS %>% 
  filter(year == 2015) 
sites.2015 <- unique(sites.2015$Station)

sites.2016 <- simpleRIBS %>% 
  filter(year == 2016) 
sites.2016 <- unique(sites.2016$Station)

length(sites.2007)
length(sites.2008)
length(sites.2009)
length(sites.2010)
length(sites.2011)
length(sites.2012)
length(sites.2013)
length(sites.2014)
length(sites.2015)
length(sites.2016)

# write.table(simpleRIBS, file="simpleRIBS_yr.csv",sep=",", row.names = FALSE)


```

Analyzing parameter and fraction issues
```{r}
# List unique parameters
paramlist <- sort(unique(simpleRIBS$Parameter))

# List unique parameters that have an "NA" fraction in their parameter names
NAfractions <- simpleRIBS %>% 
  filter(str_detect(Parameter, "NA")) %>% 
paramlist.NAfractions <- data.frame(unique(NAfractions$Parameter))
```


Remove unwanted parameters from table
```{r}
# Andreas says to remove p-Bromoflourobenzene 1,2, dichlororethane D4, and Toluene D-8 (total %)- these are internal standards not an environmental measurement. 
# Remove lab-measured DO, pH, and temperature from final table posted to data portal!

simpleRIBS.RMparams <- filter(simpleRIBS, 
 !Parameter %in% 
   c("p-Bromofluorobenzene (total,%)", "1,2-Dichloroethane-D4 (total,%)", "Toluene-D8 (total,%)"))

```

Use casewhen to normalize parameter naming conventions
```{r}
# Also fix T,D issues here once solved

```

Separate param field into param, fraction, and unit
# No need to do this. These are separate in RIBS.csv. But maybe keep these combined for data portal table.
```{r}
# Look for last open parenthese? Some contain two sets.
# Then separate by comma

```

Convert params with multiple units to single, based on what ALS reports now.
```{r}

```

Import 2016 Mohawk data 
```{r}
# Do this in a separate Rmd. Need to rectify station IDs and parameters...
# Create a master table for this data with all old and new fields.
```

Merge new and existing SiteIDs
```{r}
# First double check work and notes form working with Di and Brian.
# Need to add "new" (80) sites to sites table.
# Replace site names with ones from master sites table?
# Remove lat/long fields from table, or replace with that from sites table

```

Add additional fields to prep for new data input
```{r}
# Add flag field (and historic data flag), other fields to be populated for new data.

```

